usage: sh adam.sh benchCAV2019 [-circ] [-d] -i <file> [-l <file>] [-max <arg>] [-o <file>] [-p
       <abcParameters>] [-psst] [-stats] [-t] [-v] [-veri <verifier>]
Just for benchmark purposes. Model checks nets and formulas for CAV 2019.
 -circ,--circuit                      Saves the created circuit of the net as PDF.
 -d,--debug                           Get some debug infos.
 -i,--input <file>                    The path to the input file in APT format, which should
                                      be examined.
 -l,--logger <file>                   The path to an optional logger file. If it's not set,
                                      the information will be send to the terminal.
 -max,--maximality <arg>              States which kind of maximality should be used. Possible
                                      values: IntC (interleaving calculated within the
                                      circuit)  | IntF (interleaving added to the formula)  |
                                      ConF (concurrent added to the formula)  | NONE. Standard
                                      is NONE.
 -o,--output <file>                   The path to the output file. If it's not given the path
                                      from the input file is used.
 -p,--abcParameters <abcParameters>   Parameters for the verifier / falsifier.
 -psst,--silent                       Makes the tool voiceless.
 -stats,--statistics                  Calculates and prints some statistics for the call.
 -t,--trans                           Saves the transformed net in APT format and, in the case
                                      that dot is executable, as PDF.
 -v,--verbose                         Makes the tool chatty.
 -veri,--verifier <verifier>          The verifier which should be used. Possible values: IC3
                                      | INT | BMC | BMC2 |BMC3. Standard is IC3
