usage: sh adam.sh gen_mc_smart_factory [-d] [-l <file>] -nb1 <numberOf_nb_products> -nb2
       <numberOf_nb_shared_machines> -nb3 <numberOf_nb_specific_machines> [-npdf] -o <file>
       [-psst] [-v]
Generates a smart factory which can create 'nb_products' products. There
are 'nb_shared_machines' machines which are shared by all products, and
'nb_special_machines' machines which are just responsable for the
creation of one type of product. Saves the resulting net in APT and, if dot is executable, as
pdf.
 -d,--debug                                                       Get some debug infos.
 -l,--logger <file>                                               The path to an optional
                                                                  logger file. If it's not
                                                                  set, the information will be
                                                                  send to the terminal.
 -nb1,--nb_nb_products <numberOf_nb_products>                     The desired number of
                                                                  products (>= 1).
 -nb2,--nb_nb_shared_machines <numberOf_nb_shared_machines>       The desired number of shared
                                                                  machines.
 -nb3,--nb_nb_specific_machines <numberOf_nb_specific_machines>   The desired number of
                                                                  specific machines.
 -npdf,--noPDF                                                    Does not create a pdf of the
                                                                  generated net.
 -o,--output <file>                                               The output path where the
                                                                  generated Petri net with
                                                                  flows should be saved.
 -psst,--silent                                                   Makes the tool voiceless.
 -v,--verbose                                                     Makes the tool chatty.
