Usage: sh adam.sh <module> or java -jar adam.jar <module>
Available modules:
  pnwt2dot                       Converts a Petri net with transits to a
                                 dot file.
  pnwt2pdf                       Converts a Petri net with transits to a
                                 pdf file by using Graphviz (dot has to be
                                 executable).
  sdn2dot                        Converts a Software Defined Networks
                                 topology (with an concurrent update) to a
                                 Petri net with transits and saves this to
                                 a dot file.
  sdn2pdf                        Converts a Software Defined Networks
                                 topology (with an concurrent update) to a
                                 Petri net with transits and saves this to
                                 a pdf file by using Graphviz (dot has to
                                 be executable).
  mc_pn                          Modelchecking 1-bounded Petri nets with
                                 inhibitor arcs against LTL.
  mc_pnwt                        Modelchecking Petri nets with transits
                                 against FlowLTL  or LTL.
  mc_sdn                         Modelchecking Software Defined Networks
                                 with concurrent updates.
  gen_mc_rm_node_update          Generates a network which has an update
                                 function to detour exactly one node (the
                                 node is chosen randomly). Saves the
                                 resulting net in APT and, if dot is
                                 executable, as pdf.
  gen_mc_redundant_flow_network  Generates a network which has two ways to
                                 the output. A update function can block
                                 one of the ways. This can be done in
                                 correct or incorrect ways. Saves the
                                 resulting net in APT and, if dot is
                                 executable, as pdf.
  gen_topologie_zoo              Generates a network from the topology
                                 given by the input file. Saves the
                                 resulting net in APT and, if dot is
                                 executable, as pdf.
